---
title: "DS202 Lab2: Muhammad Khairi Norizan"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Reading in the data

```{r}
library(ggplot2)
library(dplyr)
library(classdata)
data(choco)
str(choco)
```

## Searching for the Best Chocolates

We will be exploring what aspects of the chocolates may affect taste. Before setting off to the exploration, answer the following questions.

1. How are the cocoa percent distributed? Create both a histogram and a boxplot and describe them. Don't forget to mentioned outliers, if there are any.

```{r, echo=FALSE}
ggplot(choco, aes(x = CocoaPercent)) + geom_histogram(binwidth=5)
```

```{r, echo=FALSE}
ggplot(choco, aes(y = CocoaPercent)) + geom_boxplot()
```

```{r}
summary(as.numeric(choco$CocoaPercent))
```

2. How does the number of ratings depend on the country of bean origin? Draw a bar chart of the number of ratings by bean origin. **[Hint: If your graph is too dense and the labels are not legible, show fewer bean origins.]**

```{r, echo=FALSE}

country_filtered <- table(choco$CountryBeanOrigin) %>% sort(decreasing = TRUE) %>% head(10)

barplot(country_filtered, las = 2, cex.names = 0.5) 

```

3. Do ratings depend on the cocoa percentage of a chocolate bar? Create both numerical and graphical summaries, and explain. [Hint: Think about why the scatter plot is not a very good choice for visualization here]
```{r}

choco$PercentGroup <- floor(choco$CocoaPercent / 10)

boxplot(Rating~PercentGroup,data=choco)

```

4. How do different bean origin compare in terms of the flavor of chocolates? Are bean from some places better than the other? Create both numerical and graphical summaries, and explain.

```{r}
# Get the flavor and the number of each flavor 
flavor <- table(choco$Characteristics1)
# Filter only flavor that are more than 50
filteredFlavor <- flavor[flavor > 50]
choco_filtered <- filter(choco, Characteristics1 %in% names(filteredFlavor))

# Filter top 10 countries in the dataset
country_filtered <- table(choco$CountryBeanOrigin) %>% sort(decreasing = TRUE) %>% head(10)

choco %>% filter(Characteristics1 %in% names(filteredFlavor)) %>% filter(CountryBeanOrigin %in% names(country_filtered)) %>% ggplot() + geom_bar(aes(x = CountryBeanOrigin, fill = Characteristics1), position = 'fill') + coord_flip()

# Are beans from some paces better than the other?
tapply(choco$Rating, choco$CountryBeanOrigin, summary) %>%
  head(5)
```

